---
title: "said"
author: "Phillip Abbott"
date: "June 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Said:  import USIT data and un-normalize projects

```{r}

library(tidyverse)

said <- function() {
  result <- new.env(emptyenv())

  result$my_tables <- list()
    
  fn <- function(the_name, the_year) {
    read_csv( paste0("20", the_year, "/", the_name, ".csv"))
  }
  
  fn_all <- function(the_name, the_years=13:18) {
  
    result$my_tables[[the_name]] <- list()
    for (year in the_years)
      result$my_tables[[the_name]][[year]] <- fn(the_name, year)
    
  }
  
  
  # result$my_tables[["Projects"]] <- list()
  # result$my_tables[["Projects"]][[18]] <- result$fn("Projects", 18)
  
  fn_all("Projects")
  fn_all("Activities")
  fn_all("BusinessCase", 16:18)
  result
  
  # where you were:  read in for each of the available files.  
  # merge where possible:  expand to NA
  # do the joins
  
}

# Projects18 <- read_csv("2018/Projects.csv")

# Projects18 %>% colnames()


q0 <- said()

q0 %>% ls.str()

```


```{r}

# q0$my_tables$Projects[[17]] %>% colnames( ) %>% setdiff(q0$my_tables$Projects[[18]] %>% colnames( ))

my_nice_col_names <- c(

 "Unique Investment Identifier",   "Business Case ID"               ,"Agency Code"                   
 ,"Agency Name"                  ,  "Investment Title"               ,"Unique Project ID"             
 ,"Project ID"                    , "Agency Project ID"              ,"Project Name"                  
 ,"Objectives / Expected Outcomes", "Start Date"                     ,"Completion Date"               
 ,"Project Life Cycle Cost"        ,"SDLC Methodology"                              
 ,"Release Every Six Mo"           ,"Release Every Six Mo Comment"           
 ,"Schedule Variance (in days)"    ,"Schedule Variance (%)"          ,"Schedule Color"                
 ,"Cost Variance ($ M)"            ,"Cost Variance (%)"              ,"Cost Color"                    
 ,"Project Status"                 ,"Updated Date"                   ,"Updated Time"  
)

# remember to add the year.

add_the_year <- function(the_data_frame, the_year) {
  the_new_col <- rep(the_year,times=nrow(the_data_frame))
  df <- data.frame(year=the_new_col)
  colnames(df)[1] <- "year"
  the_data_frame %>% bind_cols(df)
  
}

p16 <- q0$my_tables$Projects[[16]][, my_nice_col_names]
p16 <- p16 %>% add_the_year(16)
p17 <- q0$my_tables$Projects[[17]][, my_nice_col_names]
p17 <- p17 %>% add_the_year(17)

p17$`Updated Date` <- p17$`Updated Date` %>% as.Date("%m/%d/%Y")

p18 <- q0$my_tables$Projects[[18]][, my_nice_col_names]
p18 <- p18 %>% add_the_year(18)
p18$`Updated Date` <- p18$`Updated Date` %>% as.Date("%m/%d/%Y")


punt <- function(the_data_frame, the_column_name) {
  the_new_col <- rep(NA,times=nrow(the_data_frame))
  df <- data.frame(the_column_name=the_new_col)
  colnames(df)[1] <- the_column_name
  the_data_frame %>% bind_cols(df)
}


p14 <- q0$my_tables$Projects[[14]]
p14 <- p14 %>% punt("Project Life Cycle Cost" )
p14 <- p14 %>% punt("SDLC Methodology" )
p14 <- p14 %>% punt("Release Every Six Mo" )
p14 <- p14 %>% punt("Release Every Six Mo Comment" )
p14 <- p14 %>% punt("Project Status" )
p14 <- p14[, my_nice_col_names]
p14 <- p14 %>% add_the_year(14)

p15 <- q0$my_tables$Projects[[15]]
p15 <- p15 %>% punt("Project Life Cycle Cost" )
p15 <- p15 %>% punt("SDLC Methodology" )
p15 <- p15 %>% punt("Release Every Six Mo" )
p15 <- p15 %>% punt("Release Every Six Mo Comment" )
p15 <- p15 %>% punt("Project Status" )
p15 <- p15[, my_nice_col_names]
p15 <- p15 %>% add_the_year(15)


pcombined <- p14
pcombined <- pcombined %>% bind_rows(p15)
pcombined <- pcombined %>% bind_rows(p16)
pcombined <- pcombined %>% bind_rows(p17)
pcombined <- pcombined %>% bind_rows(p18)

pcombined %>% write.csv("projects_combined.csv")

```
> my_nice_col_names %>% setdiff( q0$my_tables$Projects[[15]] %>% colnames() )
[1] "Project Life Cycle Cost"      "SDLC Methodology"             "Release Every Six Mo"        
[4] "Release Every Six Mo Comment" "Project Status"   



# Activities

ok now that we have projects can we get activities.

```{r}
#  q0$my_tables$Activities[[17]] %>% colnames()


my_nice_activity_col_names <- c(
  
 "Unique Investment Identifier"  ,"Business Case ID"             ,"Agency Code"                 
 ,"Agency Name"                  ,"Investment Title"             ,"Agency Activity ID"          
 ,"Project ID"                   ,"Activity Name"                ,"Activity Description"        
 ,"Structure ID"                 
 ,"Start Date Planned"           ,"Start Date Projected"         ,"Start Date Actual"           
 ,"Completion Date Planned"      ,"Completion Date Projected"    ,"Completion Date Actual"      
 ,"Total Costs Planned ($M)"     ,"Total Costs Projected ($M)"   ,"Total Costs Actual ($M)"     
 ,"Schedule Variance (in days)"  ,"Schedule Variance Percent"    ,"Schedule Duration (in days)" 
 ,"Cost Variance ($M)"           ,"Cost Variance Percent"        ,"Activity Status"             
 ,"Has No Child Activity"        
 ,"Baseline ID"                  ,"Unique Activity ID"          
)

cn <- function(n)  q0$my_tables$Activities[[n]] %>% colnames()

cnn <- function(n) my_nice_activity_col_names %>% setdiff(cn(n))

get_activity <- function(n) {
  a14 <- q0$my_tables$Activities[[n]]
  a14 <- a14[, my_nice_activity_col_names]
  a14 <- a14 %>% add_the_year(n)
  a14
}

a14 <- get_activity(14)
a14$`Agency Activity ID` <- a14$`Agency Activity ID` %>% as.integer() 


a15 <- q0$my_tables$Activities[[15]]
a15 <- a15 %>% punt("Has No Child Activity" )
a15$`Agency Activity ID` <- a15$`Agency Activity ID` %>% as.integer() 
a15 <- a15[, my_nice_activity_col_names]
a15 <- a15 %>% add_the_year(15)

a16 <- get_activity(16)
a16$`Agency Activity ID` <- a16$`Agency Activity ID` %>% as.integer() 
a17 <- get_activity(17)
a17$`Agency Activity ID` <- a17$`Agency Activity ID` %>% as.integer() 
a17$`Start Date Planned` <- a17$`Start Date Planned` %>% as.character()
a17$`Completion Date Planned` <- a17$`Completion Date Planned` %>% as.character()
a17$`Start Date Projected` <- a17$`Start Date Projected` %>% as.character()
a17$`Completion Date Projected` <- a17$`Completion Date Projected` %>% as.character()
a17$`Start Date Actual` <- a17$`Start Date Actual` %>% as.character()
a17$`Completion Date Actual` <- a17$`Completion Date Actual` %>% as.character()
a17$`Has No Child Activity` <- a17$`Has No Child Activity` %>% as.integer()
a18 <- get_activity(18)
a18$`Agency Activity ID` <- a18$`Agency Activity ID` %>% as.integer()
a18$`Start Date Planned` <- a18$`Start Date Planned` %>% as.character()
a18$`Completion Date Planned` <- a18$`Completion Date Planned` %>% as.character()
a18$`Start Date Projected` <- a18$`Start Date Projected` %>% as.character()
a18$`Completion Date Projected` <- a18$`Completion Date Projected` %>% as.character()
a18$`Start Date Actual` <- a18$`Start Date Actual` %>% as.character()
a18$`Completion Date Actual` <- a18$`Completion Date Actual` %>% as.character()
a18$`Has No Child Activity` <- a18$`Has No Child Activity` %>% as.integer()

acombined <- a14
acombined <- acombined %>% bind_rows(a15)
acombined <- acombined %>% bind_rows(a16)
acombined <- acombined %>% bind_rows(a17)
acombined <- acombined %>% bind_rows(a18)

acombined %>% write.csv("activities_combined.csv")

```


# All together now


```{r}

activities_and_projects <- acombined %>% left_join(pcombined, by=c("Project ID", "year"))

activities_and_projects %>% write.csv("activities_joined_with_project.csv")

```



# Business Cases

```{r}

bc <- function(n)  q0$my_tables$BusinessCase[[n]] %>% colnames()

my_nice_business_case_col_names <- bc(16) %>% intersect(bc(17)) %>% intersect(bc(18))

get_bus_case <- function(n) {
  bc <- q0$my_tables$BusinessCase[[n]]
  bc <- bc[, my_nice_business_case_col_names]
  bc <- bc %>% add_the_year(n)
  bc
}

bc16 <- get_bus_case(16)
bc16$`Date of Last Update to CIO Evaluation` <- bc16$`Date of Last Update to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Change to CIO Evaluation` <- bc16$`Date of Last Change to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Baseline` <- bc16$`Date of Last Baseline` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Change to Activities` <- bc16$`Date of Last Change to Activities` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Update to Activities` <- bc16$`Date of Last Update to Activities` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Change to Performance Metrics` <- bc16$`Date of Last Change to Performance Metrics` %>% as.Date("%m/%d/%Y")
bc16$`Date of Last Update to Performance Metric Actuals` <- bc16$`Date of Last Update to Performance Metric Actuals` %>% as.Date("%m/%d/%Y")
bc16$`Investment Auto Submission Date` <- bc16$`Investment Auto Submission Date` %>% as.Date("%m/%d/%Y")


bc17 <- get_bus_case(17)
bc17$`Date of Last Update to CIO Evaluation` <- bc17$`Date of Last Update to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Change to CIO Evaluation` <- bc17$`Date of Last Change to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Baseline` <- bc17$`Date of Last Baseline` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Change to Activities` <- bc17$`Date of Last Change to Activities` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Update to Activities` <- bc17$`Date of Last Update to Activities` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Change to Performance Metrics` <- bc17$`Date of Last Change to Performance Metrics` %>% as.Date("%m/%d/%Y")
bc17$`Date of Last Update to Performance Metric Actuals` <- bc17$`Date of Last Update to Performance Metric Actuals` %>% as.Date("%m/%d/%Y")
bc17$`Investment Auto Submission Date` <- bc17$`Investment Auto Submission Date` %>% as.Date("%m/%d/%Y")

bc18 <- get_bus_case(18)
bc18$`Date of Last Update to CIO Evaluation` <- bc18$`Date of Last Update to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Change to CIO Evaluation` <- bc18$`Date of Last Change to CIO Evaluation` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Baseline` <- bc18$`Date of Last Baseline` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Change to Activities` <- bc18$`Date of Last Change to Activities` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Update to Activities` <- bc18$`Date of Last Update to Activities` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Change to Performance Metrics` <- bc18$`Date of Last Change to Performance Metrics` %>% as.Date("%m/%d/%Y")
bc18$`Date of Last Update to Performance Metric Actuals` <- bc18$`Date of Last Update to Performance Metric Actuals` %>% as.Date("%m/%d/%Y")
bc18$`Investment Auto Submission Date` <- bc18$`Investment Auto Submission Date` %>% as.Date("%m/%d/%Y")


bccombined <- bc16
bccombined <- bccombined %>% bind_rows(bc17)
bccombined <- bccombined %>% bind_rows(bc18)


```




# All together + Business Case


```{r}


activities_and_projects_and_business_case <- activities_and_projects %>% left_join(bccombined, by=c("Business Case ID.x"="Business Case ID", "year"))

activities_and_projects_and_business_case %>% write.csv("activities_joined_with_projects_joined_with_business_case.csv")

```


# clean up some duplication

```{r}

a0 <- activities_and_projects_and_business_case

a0  %>% colnames() %>% sort()

eq <- function(lhs, rhs) {
  if (is.na(lhs) && is.na(rhs)) return(true)
  lhs==rhs
}

a0 $`Agency Code` %>%eq( a0$`Agency Code.x`)

my_check <- function(a, b) ( a0[,a] == a0[,b]) %>% all()

mc2 <- function(a) my_check(paste0(a,".x"), paste0(a,".y"))

mc2( "Unique Investment Identifier")



ap0 <- activities_and_projects

ap0 <- ap0 %>% select(-"Agency Code.y")
ap0 <- ap0 %>% rename("Agency Code"= "Agency Code.x")

ap0 <- ap0 %>% select(-"Agency Name.y")
ap0 <- ap0 %>% rename("Agency Name"= "Agency Name.x")

ap0 <- ap0 %>% select(-"Business Case ID.y")
ap0 <- ap0 %>% rename("Business Case ID"= "Business Case ID.x")



ap0 <- ap0 %>% select(-"Unique Investment Identifier.y")
ap0 <- ap0 %>% rename("Unique Investment Identifier"= "Unique Investment Identifier.x")


activities_and_projects_and_business_case <- ap0 %>% left_join(bccombined, by=c("Business Case ID", "year"))

activities_and_projects_and_business_case %>% write.csv("activities_joined_with_projects_joined_with_business_case.csv")


```


 [6] "Agency Code.x"                                    
 [7] "Agency Code.y"                                    
 [9] "Agency Name.x"                                    
[10] "Agency Name.y"                                    
[17] "Business Case ID.x"                               
[18] "Business Case ID.y"                               
 
[78] "Unique Investment Identifier.x"                   
[79] "Unique Investment Identifier.y"                   
   
# Cleaning up APB

```{r}

apb0 <- activities_and_projects_and_business_case

my_check3 <- function(a, b) ( apb0[,a] == apb0[,b]) %>% all()

mc3 <- function(a) my_check3(paste0(a,".x"), paste0(a,".y"))

mc3( "Agency Name")


```






# on the day of 

* Create Faux numeric columns
* generate clustering

```{r}

library(stats)
library(tidyverse)
library(class)

g_size = 99
idx <- 1:g_size
fib_ <- c(0,1, 2, 3, 5, 8)
fib <- function() sample(fib_, g_size, TRUE)
ct <- function() (runif(g_size) * 1000) %>% floor()
the_data_frame <- data.frame(idx=idx, holy=fib(), grail=fib(), life=fib(), brian=fib(), cost=ct(), schedule=ct())




q0 <- kmeans(the_data_frame[,2:5],2)

the_data_frame <- the_data_frame %>% cbind(cluster=q0$cluster)

plot( the_data_frame$schedule ~ the_data_frame$cost,col=the_data_frame$cluster )

the_data_frame %>% write.csv("faux_clustering.csv")

```



# now do the same thing except for KNN 

```{r}

library(tidyverse)

g_size = 99
idx <- 1:g_size
fib_ <- c(0,1, 2, 3, 5, 8)
fib <- function() sample(fib_, g_size, TRUE)
ct <- function() (runif(g_size) * 1000) %>% floor()



the_training_set <- data.frame(idx=idx, holy=fib(), grail=fib(), life=fib(), brian=fib(), cost=ct(), schedule=ct())

the_test_set <- data.frame(idx=idx, holy=fib(), grail=fib(), life=fib(), brian=fib(), cost=ct(), schedule=ct())


get_category <- function(cost, schedule) {
  if (cost > 500 && schedule > 500) return(4)
  if (cost < 500 && schedule < 500) return(1)
  if (cost > 500) return (3)
  2
}

the_categories <- 1:g_size
for (k in 1:g_size) the_categories[k] <- get_category(the_training_set$cost[k], the_training_set$schedule[k])


the_training_set <- the_training_set %>% cbind(category=the_categories)

knn(the_training_set[,2:5], the_test_set[,2:5], the_categories)

plot()

```



# OK, lets looks at the n-grams
## START HERE

```{r}

library(tidyverse)
library(stats)
library(readr)

wwc <- read_csv("with_word_counts_v3.csv")


colnames(wwc)

wwc0 <- wwc[, c(8, 30, 20,23, 81:240)]

# don't worry about stuff for which we possess no cost or schedule data
wwc0 <- wwc0[!is.na(wwc0$`Total Costs Actual ($M)`),]
# kill the outliers just to make it look better
wwc0 <- wwc0[wwc0$`Total Costs Actual ($M)` < 1000, ]
wwc0 <- wwc0[!is.na(wwc0$`Schedule Duration (in days)`),]


q0 <- kmeans(wwc0[,5:43],2)

plot(wwc0$`Total Costs Actual ($M)`~wwc0$`Schedule Duration (in days)`, col=q0$cluster)

q0$centers

write.csv(q0$centers, "centers2.csv")

```


# no really we have to have good categories

```{r}

cs0 <- wwc0$`Total Costs Actual ($M)` %>% summary()
ss0 <- wwc0$`Schedule Duration (in days)` %>% summary()

# use 3rd quartile as a cutoff
cost_cutoff <- 1.04
schedule_cutoff <- 190

# need more granular categories

get_quartile <- function(s, x) {
  # s <- pop%>% summary()
  s25 <- s[2]
  s50 <- s[3]
  s75 <- s[5]
  
  if (x < s25) return(1)
  if (x < s50) return(2)
  if (x < s75) return(3)
  4
}


cost_summary      <- wwc0$`Total Costs Actual ($M)`     %>% summary()
schedule_summary  <- wwc0$`Schedule Duration (in days)` %>% summary()


get_category <- function(cost, schedule) {

c <- cost_summary %>% get_quartile(cost)
s <- schedule_summary %>% get_quartile(schedule)

c*s
  
}

t0 <- 1:( wwc0 %>% nrow() )
the_category <- t0 %>% map( function(k) get_category( wwc0$`Total Costs Actual ($M)`[k], wwc0$`Schedule Duration (in days)`[k])) 

the_category <- the_category %>% unlist()


```


{azure trial license = qdwyy88zx5jzebucfz}


government united modelling budgets yested 
```{r}
# 87k items.

n0 <- 1000

s0 <- 10

t0 <- 1:n0+1

the_training_set <- wwc0[t0,]
the_test_set <- wwc0[1:(2*n0+1),]


q0 <- class::knn(the_training_set[,5:(10*s0)], the_test_set[,5:(10*s0)], the_category[t0], k=s0)

q0 %>% table() %>% pie()

my_colorsa <- heat.colors(16)
my_colorsb <- topo.colors(16)
my_colors <- c(topo.colors(8), heat.colors(8) )

plot(log(the_test_set$`Total Costs Actual ($M)`)~log(the_test_set$`Schedule Duration (in days)`),
    main='Clustering', xlab='Duration', ylab='Cost', col=my_colors[q0] )




```





```{r}


q1 <- q0[t0] %>% as.numeric()


x0 <- log(the_test_set$`Schedule Duration (in days)`[q1>1])
y0 <- log(the_test_set$`Total Costs Actual ($M)`[q1>1])



points( x0, y0 , pch='x', col='blue', cex=2)



it0 <- ((q1>2) %>% which())[1]
x0 <- log(the_test_set$`Schedule Duration (in days)`[it0])
y0 <- log(the_test_set$`Total Costs Actual ($M)`[it0])



points( x0, y0 , pch=17, col='red', cex=3)


```



# Later:  week 27

make a database column based on the column of the table.



```{r}

ppsql <- function(the_table_name) {
  result <- new.env(emptyenv())
  
  kill <- function(it, s, target='') gsub(s,target, it, fixed=TRUE)
  
  bad_characters <- c(' ', '(', ')', '$', '.', ',', '%')
  
  get_safe_name <- function(it) {
    for (k in bad_characters) it <- it %>% kill(k, '_')
    it
  }
  
  enquote <- function(it) paste0('"', it, '"')
  result$make_column <- function(the_column_name, the_type='character varying') {
    the_column_name <- the_column_name %>% get_safe_name()
    paste('ALTER TABLE', paste0('public.', the_table_name %>% enquote()), 'ADD COLUMN', the_column_name %>% enquote(), the_type , ';')
  }
  
  result
}


p01 <- ppsql('R02')
'asdf' %>% p01$make_column() %>% writeLines()

# ALTER TABLE public."Risks01" ADD COLUMN "Description" character varying;


```


## now do it for Activities[[18]].

```{r}

sink('make_activity_18.sql')

q0$my_tables$Activities[[18]] %>% colnames() %>% map( p01$make_column ) %>% unlist() %>% writeLines()

sink()

```



SELECT 
  count(distinct "Activities18"."Agency_Activity_ID"), count("Activities18"."Agency_Activity_ID") 
FROM 
  public."Activities18" where "Activities18"."Agency_Activity_ID" ~ '^.10$' limit 19;


```{r}

library(odbc)
con <- dbConnect(odbc::odbc(), .connection_string = "Driver={PostgreSQL Unicode};Database=mcfc01")
```

```{sql connection=con}

-- ALTER TABLE public."Activities18" ADD COLUMN "Agency_Activity_ID_int" bigint;
-- ALTER TABLE public."Activities18" ADD COLUMN "Agency_Code_int" bigint;

UPDATE  public."Activities18" set "Agency_Activity_ID_int" = "Agency_Activity_ID"::int;  
UPDATE  public."Activities18" set "Agency_Code_int" = "Agency_Code"::int;  

SELECT count(*) from "public"."Activities18";


```







```{r}

 

 

 

f2 <- function(n=9, f0=function(nn) 1/nn, a=1) {

 

  result <- new.env(emptyenv())

 

  fn <- function(nn ) c( a*( 1-f0(nn) ),  a*( 1+f0(nn) ))

 

  t0 <- 1:n

  x0 <- t0 %>% fn()

  x0 <- c(a,x0)

  x0 <- x0 %>% sort()

 

  result$plotme <- function() {

    x0 %>% plot(col='white')

    x0 %>% map( function(it) abline(h=it))

  }

 

  

  

  

  

  

  

  

  ff <- function(n, by=16) {

    a <- floor(n)

    n <- n - a

    n <- by*n

    n <- round(n)

    c(whole=a,sixteents=n)

  }

 

  result$get_points <- function(by=16) {

    whole_part=floor(x0)

    x0 <- x0 - whole_part

    x0 <- x0*by

    x0 <- round(x0)

   

    data.frame(whole_part=whole_part, fractional_part=x0)

 

  }

 

  result

 

}

 

q0 <- f2()

 

q0$plotme()

 

```

 

 

 

 

```{r}

 

 

phi <- (sqrt(5)-1)/2

 

 

q0 <- f2(9,function(n) phi^(n-1), a=3)

 

q0$plotme()

 

q0$get_points()

 

```

 

Best regards,

 

Phillip Abbott

 

phillip.abbott@shell.com

Work:      020 3023 3205

Cell:      079 4935 0714

 





